---
title: "Data modeling - session 9"
author: "BAO YEN HO"
date: "01/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://maria-pro.github.io/bco7000/sessions/session9/slides.html#2

# co-variation
Negative relationship
zero-relationship <- independent variables

```{r}
library(tidyverse)
library(scales)
theme_set(theme_light()) #check in 'Help'
```

# Exploratory data analysis
```{r}
data(diamonds)
```

```{r}
diamonds%>%
  ggplot(aes(cut, binwidth=0.5)
         )+
  geom_bar(fill="orange")

diamonds%>%
  ggplot(aes(color, binwidth=0.6)
         )+
  geom_bar(fill="blue")

diamonds%>%
  ggplot(aes(clarity, binwidth=0.4)
         )+
  geom_bar(fill="red")

diamonds%>%
  ggplot(aes(price, binwidth=0.4)
         )+
  geom_histogram(fill="darkgreen")

diamonds%>%
  ggplot(aes(carat)
         )+
  geom_histogram(fill="darkblue")
```
```{r}
data(faithful)
```

```{r}
diamonds%>%
  ggplot(aes(y)
         )+
  geom_histogram(binwidth=0.5, fill="darkred")

diamonds%>%
  ggplot(aes(y)
         )+
  geom_histogram(fill="darkred")
```
# geom_boxplot
```{r}
diamonds%>%
  ggplot(aes(cut, price)
  )+
  geom_boxplot()
```
```{r}
data(mpg)
```

```{r}
mpg%>%
  ggplot(aes(x=reorder(class, hwy, FUN=median), y=hwy)
    )+
  geom_boxplot()
```
```{r}
diamonds%>%
  ggplot(aes(cut, color))+
  geom_count()
```
Alpha = transparency

## Modeling
Models = show the systematic relationship b/w different variables
Models = regression models
       = classification models (categories variables)

### Linear regression
```{r}
#install.packages("readxl")
library(readxl)
ageandheight <- read_excel("ageandheight.xls", sheet = "Hoja2") #to import .xls data
```

# Run regression (lm=linear regression)
```{r}
lmHeight2<-lm(height~age + no_siblings, data = ageandheight) #to predict the height based on the age and no_Sibling
summary(lmHeight2)
# we see the formula that we wrote, coefficients for each dependent variable: 'age` is positive and `no_siblings` is big number of negative means it is a critical factor.
```

