---
title: "Session4"
author: "BAO YEN HO"
date: "14/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data wrangling exercises

**YEAH**
dplyr is a grammar of data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges:

    mutate() adds new variables that are functions of existing variables
    select() picks variables based on their names.
    filter() picks cases based on their values.
    summarise() reduces multiple values down to a single summary.
    arrange() changes the ordering of the rows.


```{r}
library(tidyverse)
library(janitor)
avocado<-read_csv("avocado.csv")
avocado%>%head()
avocado<-avocado%>%
  janitor::clean_names()

```

We did 'filter()'
'arrange()' for sorting variables

```{r}
avocado%>%
  arrange(average_price)%>%
  head()
```

Let's change the order
```{r}
avocado%>%
  arrange(desc(average_price))%>%
  head()
```

Let's 'select()'
```{r}
dim(avocado)
avocado_short<-avocado%>%
  select(date, average_price, total_volume)
```
```{r}
avocado%>%select(date, average_price, total_volume)

avocado%>%select(-average_price) #to exclude variables

avocado%>%rename(extra_small=x4046) #To rename variables

avocado_short1<-avocado%>%
  select(date, average_price, total_volume, region)%>%
  mutate(total_price=average_price*total_volume)
rm(avocado_short2)

avocado_short1%>%head()

avocado_short1<-avocado%>%
  select(date, average_price, total_volume, region)%>%
  transmute(total_price=average_price*total_volume)#to show only new column created

avocado%>%
  group_by(type, year, region)%>%
  summarise(mean_price=mean(average_price), max_price=max(average_price))

avocado_tr<-avocado%>%
  group_by(type, year, region)%>%
  summarise(mean_price=mean(average_price), max_price=max(average_price))%>%
  ungroup()

avocado_tr%>%
  count(year)

avocado_tr%>%
  count(year, region)

avocado_tr%>%
  add_count(year, region)
```

